Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-05-21 ThesisJP/Introduction/introduction.tex

\section{Motivation}
A rapid development in computer game technology and accompanying programming languages have recently provided researchers with small personal super computers, comprised in a single graphics card (\nom{GPU}{Graphics processing unit}). The latest graphics cards\footnote{As of January 2014.} from both \nom{Nvidia}{Graphics card vendor} and \nom{AMD}{Graphics card vendor} provide more than 5 T\nom{FLOPS}{Floating point operations per second} single precision and 1.5 TFLOPS double precision computations. For double precision, this is more than the world's most powerful supercomputer could provide in 1998, and that was a room full of computers.

@@

The Capon beamformer in ultrasound imaging is a good example of an algorithm that has been widely studied over the last decade where the number of calculations was thought to be too high for real-time processing. To achieve real-time processing for e.g. cardiac ultrasound imaging, an effective processing rate of hundreds of GFLOPS is required. This number, as explained in Section \ref{sec:adaptbf}, also grows with larger subarrays and an increasing number of samples per second. Nevertheless, with modern GPUs, this amount of processing is finally available within a single card. When researchers are exploring new algorithms for ultrasound imaging, it is important to keep the architecture of parallel accelerators in mind. If a new complex algorithm is supposed to run in real time, it needs to fit the programmable and parallel pipeline of modern ultrasound scanners.

>>>>

\section{Motivation}
A rapid development in computer game technology and accompanying programming languages have recently provided researchers with small personal supercomputers, comprised in a single graphics card (\nom{GPU}{Graphics processing unit}). The latest graphics cards\footnote{As of January 2014.} from both \nom{Nvidia}{Graphics card vendor} and \nom{AMD}{Graphics card vendor} provide more than 5 T\nom{FLOPS}{Floating point operations per second} single precision and 1.5 TFLOPS double precision computations. For double precision, this is more than the world's most powerful supercomputer could provide in 1998, and that was a room full of computers.

@@

The Capon beamformer in ultrasound imaging is a good example of an algorithm that has been widely studied over the last decade where the number of calculations was thought to be too high for real-time processing to happen in near future. To achieve real-time processing for e.g. cardiac ultrasound imaging, an effective processing rate of hundreds of GFLOPS is required. This number, as explained in Section \ref{sec:adaptbf}, also grows with larger subarrays and an increasing number of samples per second. Nevertheless, with modern GPUs, this amount of processing is finally available within a single card. When researchers are exploring new algorithms for ultrasound imaging, it is important to keep the architecture of parallel accelerators in mind. If a new complex algorithm is supposed to run in real time, it needs to fit the programmable and parallel pipeline of modern ultrasound scanners.
